### 2011-12-09 AffineLieAlgebras/Thesis/concl.tex
Thesis work
Thesis partially structure cleaned, some translations in chapter 2.
Minor changes

\review

>>>>

\conclusion
\label{cha:conclusion1}

\section*{Acknowledgements}
\label{sec:acknowledgements}
I thank the organizers of The Seventh International Conference ``Quantum Theory and Symmetries'' (QTS-7) for the opportunity to present this work and especially professor C. Burdik for his attention. I am grateful to A. Bytsko, K. Izyurov, D. Chelkak and R. Santachiara for the discussions on SLE and WZNW models. This work  is supported by
the Chebyshev Laboratory (Department of Mathematics and Mechanics,
Saint-Petersburg State University) under the grant 11.G34.31.0026
of the Government of the Russian Federation.
